### 2014-11-12 tex/heap.tex
Minor word changes

\textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
\]
$\cfgnt{L}^\leftarrow$ is the pre-image of the location
map. Informally, any two constraint location pairs connected to a
common reference form a contradiction: only one can be true in any
satisfying assignment. The property means that a satisfying assignment
resolving aliasing relationships results in a deterministic heap: a
field access returns a single location.

\noindent\textbf{Type consistency}: all locations associated with a reference have the same type.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
\end{array}
\]

@@

The reference partitions merit further discussion as they are a
central contribution of this work. The heap summary algorithm creates
many references that are auxiliary literals or stack literals to
define the structure of the bipartite graph.  It reserves input heap
reference for constraints expressing potential aliasing. A solver
reasons over the aliasing relationships, and a satisfying assignment
uniquely identifies active edges in the graph. Those active edges
describe a concrete heap and its shape.

>>>>

\textbf{Determinism}: a reference in  $(\cfgnt{L}\ \cfgnt{R})$ cannot point multiple locations simultaneously.
$$
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
\end{array}
$$
$\cfgnt{L}^\leftarrow$ is the pre-image of the location
map. Informally, any two constraint location pairs connected to a
common reference form a contradiction: only one can be true in any
satisfying assignment. The property means that a satisfying assignment
resolving aliasing relationships results in a deterministic heap: a
field access returns a single location.

\textbf{Type consistency}: all locations associated with a reference have the same type.
\[
\begin{array}{l}
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (\\
\ \ \ \ (\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))
\end{array}
\]

@@

The reference partitions merit further discussion as they are a
central to the proofs. The heap summary algorithm creates
many references that are auxiliary literals or stack literals to
define the structure of the bipartite graph.  It only uses input heap
references for constraints expressing potential aliasing. A solver
reasons over the aliasing relationships, and a satisfying assignment
uniquely identifies active edges in the graph. Those active edges
describe a concrete heap and its shape.
